Reduced plasticity and variance in physiological rates for terrestrial ectotherm populations under climate change

### 2024-01-06 ms.qmd
Fix trait fig to remove extra legends.

ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
                              "Metabolic_enzyme" = "Metabolic Enzymes",
                              "Rest_MR" = "Resting Metabolic Rate",
                              "Max_MR" = "Maximum Metabolic Rate",
                              "Mito_oxidation" = "OXPHOS")) + theme_classic() 
#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
                              "Metabolic_enzyme" = "Metabolic Enzymes",
                              "Rest_MR" = "Resting Metabolic Rate",
                              "Max_MR" = "Maximum Metabolic Rate",
                              "Mito_oxidation" = "OXPHOS")) + theme_classic()
#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

>>>>

ptm <- orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
                              "Metabolic_enzyme" = "Metabolic Enzymes",
                              "Rest_MR" = "Resting Metabolic Rate",
                              "Max_MR" = "Maximum Metabolic Rate",
                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(legend.position = "none")
#ptm$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy

ptf <- orchard_plot(model1.3_f_het, mod = "trait_category", at = list(type = c("acute", "acclim")), by = "type", group = "record_num", weights = "prop",  xlab = TeX("$lnRR_{Q_{10}}$"), angle = 0, condition.lab = "Type") +
  scale_x_discrete(labels = c("Mito_leak" = "Proton Leak",
                              "Metabolic_enzyme" = "Metabolic Enzymes",
                              "Rest_MR" = "Resting Metabolic Rate",
                              "Max_MR" = "Maximum Metabolic Rate",
                              "Mito_oxidation" = "OXPHOS")) + theme_classic() + theme(legend.position = "none")
#ptf$layers[[1]] <- NULL # Lets just remove the data point geom layer as it's too busy
